---
title: "Developing Data Products"
author: "Eliza"
date: "December 15, 2015"
output: ioslides_presentation
---

## What the App does 

The app allows you to create a scatterplot of the price, x length, y length, and z length variables. You can choose which of the 4 variables you want to be your x and y axis by using the selection menus. You can also examine how the scatterplot changes depending on the cut quality of the diamonds. You can select as many cut qualities as you would like in the check box menu. Once you have chosen your inputs you can view the scatterplot in the main panel. 

The app can be found here: https://eliza-908.shinyapps.io/DevDataProducts

## Why My App Is Useful 

- Compare the different types of diamond cuts side by side
- See trends in prices with size of diamond 
- Assess trends in the shapes of different diamond types 

## Examining the Dataset 

```{r, echo=FALSE}
library(ggplot2)
```
```{r}
head(diamonds)
```

We see this dataset with `r nrow(diamonds)` entries of diamonds, and it measures `r ncol(diamonds)` different variables each. 

## A Typical Plot Made Easily in My App 

```{r, echo=FALSE}
p <- ggplot(diamonds, aes(x = diamonds$x, y = diamonds$price)) + geom_point(aes(color = factor(diamonds$cut)))
print(p)
```

